\documentclass[oneside,spanish,10pt, a4paper]{memoir}
%You can also try with letterpaper
\usepackage[color=6c00a4]{mucv}
%\selectcolormodel{gray} %Uncomment to look it in blanc et noir

%%%%%%%%%%%%%%% Here you put your details %%%%%%%%%%%%%%%%%%%%%%%%%%
\muSetFirstNames{First Name}
\muSetLastNames{Last Name}
\muSetAddress{Fake Street 123, Beruna 1337, Narnia.}
\muSetPhone{111-111-111}
\muSetEmail{some-mail@somedomain.com}
%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%% %%%%%%%%%%

%% Note, you can do your own page break with these commands
%\newpage
%\newgeometry{top=1.8cm,bottom=1cm,left=1.5cm,right=2cm}

\begin{document}

%Example of one section
\section{Personal Details}

%The muList environment requires a width for the first field. Play with those values.
\begin{muList}{2.4}
\muListI{Age:}{24 years old (Jan 1, 1990)}
\muListI{Nationality:}{I come from Narnia!}
\muListI{Civil Status:}{Single}
\end{muList}

\section{Education}
%The muItemU requires 4 fields, usually "Title", "Date", "Where" and a detailed description
\muItemU{MSc in Alchemy}{1997-1999}{National Autonomous University of Narnia, \textit{Narnia}}{Skills developed in spell casting and beast taming.}

%Just a filler
\section{Scientific and Technical Skills}
\begin{muList}{4.0}
\muListI{Chemistry Background:}{Development of poison, acids and life potions.}
\muListI{Physics Background:}{Electrodynamics, Mechanics, Thermodynamics and Statistical Physics.}
\muListI{Weapon Craftsmanship:}{Swords and bows is what I can offer.}
\muListI{Combat Skills:}{Dual shield wielding}
\end{muList}

\section{Work Experience}
\muItemU{Aslan's Faithful Soldier}{2009}{Aslan's Country, \textit{Narnia}}{Devoted to serve the King above all High Kings.}

%These are 2-field items, generally when when and where are not necessary
\section{Other Achievements}
\muItem{Escaped from prison in Archenland}{I wanted trial by combat, they gave me no other choice.}
\muItem{Also escaped from Calormen}{After a 2 month imprisionment, I was able to steal the key of my cell.}

\section{Languages}
\begin{muList}{2.0}
\muListI{Sindarin:}{Level C1}
\muListI{Elvish:}{Level B2}
\muListI{English:}{Native speaker.}
\end{muList}

%The normal itemize is different now.
\section{Interests}
\begin{itemize}
\setlength\itemsep{-0.1cm}
\item \small Save the world.
\item Save lives.
\item Bring happiness to the world.
\end{itemize}

\end{document}